#QUESTION 9
A farm grows grapes for jelly. The following data are measurements of sugar in the grapes of a sample
taken from each of 12 truckloads.
16.0 15.2 12.0 16.9
15.8 15.5 12.5 14.5
15.4 13.0 12.6 14.9
Assume that these are observations of a normal distributed random variable X that has mean µ and
standard deviation σ.
(a) Give point estimates of µ and σ^2.
(hint: Use MLE or MME to find the point estimators and then use the given data to find the
estimates.)
(b) Find an approximate 90% confidence interval for µ.

```{r}
grapes<-c(16,15.2,12,16.9,15.8,15.5,12.5,14.5,15.4,13,12.6,14.9)
n <- length(grapes)
samplemean <- mean(grapes)
samplesd <- sd(grapes)
critical_t <- qt(0.95,df=n-1)
margin_of_error <- critical_t*(samplesd/sqrt(n))
conf_int=c(samplemean-margin_of_error,samplemean+margin_of_error)
print(paste("mean: ", samplemean))
print(paste("standard deviation: ",samplesd))
print(conf_int)

```
#QUESTION 10
Let X equal to the length (in centimeters) of a certain species of fish when caught in the spring. A
random sample of n = 13 observations of X is Assume that these are observations of a normal distributed
13.1 5.1 18.0 8.7
16.5 9.8 6.8 12.0
17.8 25.4 19.2 15.8
23.0
random variable X that has mean µ and standard deviation σ unknown.
(a) Give a point estimate of the standard deviation σ of this species of fish.
(b) Find a 95% confidence interval for σ
```{r}
fish <- c(13.1, 5.1, 18.0, 8.7, 16.5, 9.8, 6.8, 12.0, 17.8, 25.4, 19.2, 15.8, 23.0)
samplemean <- mean(fish)
samplesd <- sd(fish)
critical_t <- qt(0.975,df=n-1)
margin_of_error <- critical_t*(samplesd/sqrt(n))
conf_int=c(samplemean-margin_of_error,samplemean+margin_of_error)
print(paste("mean: ", samplemean))
print(paste("standard deviation: ",samplesd))
print(conf_int)

```
#QUESTION 11
The I.Q. of few persons taken, at random, from a large population are recorded as
117, 119, 125, 129, 131, 132, 136, 138, 141, 120, 101, 116.
Assuming the population of scores to be normal with standard deviation= 9.9, can we believe that
the average I.Q. of corresponding population is less than 127? (Test at 5 % significance level where
Z0.05 = −1.645. ) Also find the 95% confidence interval for the population mean.
```{r}
library(BSDA)
iq <- c(117, 119, 125, 129, 131, 132, 136, 138, 141, 120, 101, 116)
pop_sd <- 9.9
result <- z.test(x = iq, mu = 127, sigma.x = pop_sd, alternative = "less", conf.level=0.95)
print(result)
```
#QUESTION 12
The heights of 10 males of a normal population are found to be
70, 67, 62, 67, 61, 68, 70, 64, 65, 66inches.
Is it reasonable to believe that the average height is greater than 64 inches? Test at 5% significance
level assuming that for 9 degrees of freedom t0.95 = 1.83.
```{r}
pop<-c(70,67,62,67,61,68,70,64,65,66)
t.test(pop, mu=64, conf.level=0.95, alternative="greater")

```

